A weakly structured stem for human origins in Africa

### 2023-01-09 paper.tex
Update paper.tex

Given this consistency in inferred recent history and the numerical challenge
of optimizing a large number of parameters, we fixed several parameters related
to recent population history so as to focus on more ancient events. These
parameters were ones supported by multiple genetic and archaeological studies.
Fixed parameters included the time of divergence between western and eastern
African populations, set to 60ka, just prior to the split of Eurasians and East
Africans set to 50ka. We also fixed the amount of admixture from Neanderthals
to Europeans directly following the out-of-Africa migration which was set to
1.5\% at 45ka (SI Section~\ref{sec:models}).

>>>>

Given this consistency in inferred recent history and the numerical challenge
of optimizing a large number of parameters, we fixed several parameters related
to recent population history so as to focus on more ancient events (SI Section {sec:models}). These
parameters were ones supported by multiple genetic and archaeological studies.
Fixed parameters included the time of divergence between western and eastern
African populations, set to 60ka, just prior to the split of Eurasians and East
Africans set to 50ka. We also fixed the amount of admixture from Neanderthals
to Europeans directly following the out-of-Africa migration which was set to
1.5\% at 45ka (SI Section~\ref{sec:models}).
